---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.retina = 2
)
library(djprlabourdash)

```

# djprlabourdash

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![R-CMD-check](https://github.com/djpr-data/djprlabourdash/workflows/R-CMD-check/badge.svg)](https://github.com/djpr-data/djprlabourdash/actions)

<!-- badges: end -->

## Overview

The `djprlabourdash` repository contains the code for the DJPR Jobs Dashboard. This dashboard is made in R with the [Shiny package](https://shiny.rstudio.com).

The dashboard provides an overview of the Victorian labour market using publicly-available data. It is created and maintained by the Data + Analytics team in DJPR Strategy and Priority Projects. **Note that all data currently displayed on the dashboard is publicly-available data.**

The [live dashboard is hosted at Shinyapps.io](https://djpr-spp.shinyapps.io/djprlabourdash/).

`djprlabourdash` is structured as an R package. This facilitates easier unit testing and code structure.

## Related repos

`djprlabourdash` depends on several related R packages:

-   [`djprdashdata`](https://github.com/djpr-data/djprdashdata) contains the data used in this app, as well as the code to update that data;

-   [`djprshiny`](https://github.com/djpr-data/djprshiny) contains common code used across DJPR Data + Analytics Shiny apps;

-   [`djprtheme`](https://github.com/djpr-data/djprtheme) is a ggplot2 theme package that implements the DJPR visualisation style guide.

## Installation

Install `djprlabourdash` and its dependencies with:

``` r
# install.packages("devtools")
devtools::install_github("djpr-data/djprlabourdash", dependencies = TRUE)
```

## Git branch structure and deployment

There are three types of branches in this repository:

1.  The `main` branch contains the code corresponding to the current live dashboard.

2.  The `dev` branch is the main working branch for the repository. This is where contributions by different people are integrated and tested before being deployed to the live dashboard.

3.  Feature branches are created by project contributors to add or modify the dashboard's functionality.

```{r, include=FALSE}
# drawn at https://app.diagrams.net/
```

![](images/djprlabourdash%20git%20branches.svg)

When any changes are made in `main`, an automatic process is triggered via GitHub Actions that re-deploys the Shiny web app - ie. the live dashboard is updated to reflect any changes made in `main`. Changes to `main` are almost always made via pull requests from `dev`. The only exception to this are urgent 'hotfix' changes made by the project administrator.

Code from project contributors is always added in 'feature branches' which are then merged into `dev`, tested, then merged into `main`.

## Folder structure and key files

Because `djprlabourdash` is structured as an R package, the folder structure reflects R package conventions. These include:

-   All functions in the package live in files ending in `.R` in the `/R` subfolder of the package.

-   Documentation for individual functions lives in `.Rd` files in the `/man` subfolder of the package. These are created automatically based on [special comments in .R files](https://r-pkgs.org/man.html?q=roxy#roxygen-comments) and should not be edited directly.

-   Code to create data used by the package ('internal data') is saved in `/data-raw`. This folder also contains some code ('scratchpads') that is used to test certain functions and can ultimately be discarded.

-   Tests that ensure functions do what they are expected to do are saved in `/tests`.

There are some other files and folders of note:

-   [DESCRIPTION](https://r-pkgs.org/description.html#pkg-description) is a file included in all R packages that descriptions what the package does, who created it, and what other packages the package depends on ('imports'). Package contributors should generally not edit this file directly - if an additional package needs to be added, use `usethis::use_package("packagename")`.

-   [NAMESPACE](https://r-pkgs.org/namespace.html?q=NAMESPACE#namespace) is another file included in all R packages. It tells R which functions from this package should be made available to users ("exported") and which functions from other packages should be available to this package ("imported"). It shouldn't be directly edited.

-   `/.github` contains code for GitHub to execute using [Github Actions](https://docs.github.com/en/actions). This includes instructions to check the package (using [R CMD check](https://r-pkgs.org/r-cmd-check.html)) to make sure that it passes all the built-in tests and does what an R package is expected to do - this is done whenever anyone initiates a pull request to the `main` or `dev` branches. It also includes instructions to deploy the dashboard to shinyapps.io whenever anything is changed in the `main` branch. Package contributors should not edit these files.

-   `/rsconnect` contains information used as part of the deployment of the dashboard to shinyapps.io. These files are created automatically and should not be directly edited.

## Code structure

As noted above, all functions live in the `/R` folder of the package. The key files for contributors to be aware of are:

-   Files starting with `viz_` contain functions to make the graphs on the dashboard.

-   Files starting with `page_` define the user interface for individual pages of the dashboard.

-   The `labour_app.R` file contains the server-side code for the Shiny app.

There are some other files related to tables and utility functions.

## Dashboard data

All data in the dashboard is publicly available. The [`djprdashdata` repository](https://github.com/djpr-data/djprdashdata) extracts this data from the ABS, minimally transforms it, and stores it. See [`djprdashdata`](https://github.com/djpr-data/djprdashdata) for further information about data extraction and storage.

### Loading dashboard data

Data is loaded into the dashboard using the function `djprlabourdash::load_dash_data()`. This function is executed once at the start of each dashboard session, ensuring any upstream change in the data is (nearly) immediately reflected on the dashboard itself.

In interactive sessions where a contributor is working with the dashboard data, the following command should be run at the beginning of the session:

```{r}
# First, run `load_all()` to ensure that this package's functions are available
# devtools::load_all()
library(djprshiny)
dash_data <- load_dash_data()
```

Note that `dash_data` is a data frame (tibble) with a nested structure. Each row of the tibble corresponds to an ABS series ID. The `data` column of the tibble contains a list of tibbles that must be unnested prior to use.

```{r}
dash_data
```

### Filtering dashboard data

Users generally work with the `dash_data` object using the `filter_dash_data()` function. This function takes a vector of ABS time series ID(s) and returned a tibble containing the corresponding data. This output is unnested for the user, meaning that project contributors can generally ignore the nested nature of `dash_data`.

A lookup table of series IDs is available from the `djprdashdata` package:

```{r}
djprdashdata::lfs_lookup
```

If a user wanted to get a data frame with the number of unemployed people in Bendigo each month from 1998 to present, they would use `filter_dash_data()` as follows:

```{r}
bendigo_unemp <- filter_dash_data("A84600028X")
bendigo_unemp
```

It is then straightforward to visualise this. We will use the `djprshiny::djpr_ts_linechart()` convenience function, which creates a ggplot2 object that generally meets our style guide:

```{r}
bendigo_unemp %>%
  djpr_ts_linechart()
```

## `viz_` files

Most contributions to the dashboard will come in the `viz_` files. These contain the code that creates the graphs on the dashboard.

Generally, each graph has its own function -- the only exception are some functions that produce multiple related graphs that are combined with `{patchwork}`.

### Naming graph functions

Graph functions all **must start with `viz_`**. The general naming convention is:

`viz_page_content_charttype()`

where:

-   `page` is an abbreviated version of the page name - like `ind` for the Indicators page;

-   `content` provides some indication of the subject of the chart, like `partrate` for a chart of the participation rate; and

-   `charttype` indicates the type of chart, such as `bar` for a bar chart.

So the `viz_ind_partrate_bar()` function, for example, produces this chart:

```{r}
djprlabourdash:::viz_ind_partrate_bar()
```

### Graph functions' arguments

**Each `viz_` function must have a first argument called `data`**. It can optionally have other arguments. **All arguments to `viz_` functions must have defaults supplied.**

Generally, the default to the `data` argument will involve a call to `filter_dash_data()`. This function takes a vector of ABS time series ID(s) and returns a dataframe containing the data corresponding to those IDs, if it is present in the data loaded into the dashboard.

These are examples of **good `viz_` functions** that satisfy these requirements:
```{r, eval=FALSE}
# This is good
viz_fake_function <- function(data = filter_dash_data("A84600028X")) {
  data %>%
    djpr_ts_linechart()
}

# This is also good
viz_fake_function <- function(data = filter_dash_data("A84600028X"),
                              min_date = as.Date("2010-01-01")) {
  data %>%
    dplyr::filter(.data$date >= min_date) %>%
    djpr_ts_linechart()
}

```

These are examples of **bad `viz_` functions** that do not satisfy the requirements:
```{r, eval=FALSE}
# THIS IS NOT OK - no data argument
viz_fake_function <- function() {
  filter_dash_data("A84600028X") %>%
    djpr_ts_linechart()
}

# THIS IS NOT OK - no default supplied to data argument 
viz_fake_function <- function(data) {
  data %>%
    djpr_ts_linechart()
}

# THIS IS NOT OK - no default supplied to min_date argument 
viz_fake_function <- function(data = filter_dash_data("A84600028X"),
                              min_date) {
  data %>%
    dplyr::filter(.data$date >= min_date) %>%
    djpr_ts_linechart()
}
```

### Graph functions' output

All `viz_` functions must return a single object, which must be a ggplot2 plot. The automated tests that are run on the package test that each `viz_` function returns a ggplot2 plot -- ie. a single object that inherits class `gg` - and these tests will fail where this is not true.

If multiple plots are returned, they should be combined using the `{patchwork}` package, which returns objects of class `gg`.

These are examples of **good `viz_` functions** that return a `gg` object:
```{r, eval = FALSE}
# This is good - returns a single ggplot2 object
viz_fake_function <- function(data = filter_dash_data("A84600028X")) {
  data %>%
    djpr_ts_linechart()
}

# This is also good - returns a single ggplot2 object
viz_fake_function <- function(data = filter_dash_data("A84600028X")) {
  my_plot <- data %>%
    djpr_ts_linechart()
  
  my_plot
}

# This is also good - returns a single ggplot2 object
viz_fake_function <- function(data = filter_dash_data("A84600028X")) {
  data %>%
    ggplot(aes(x = date, y = value)) +
    geom_line() +
    djprtheme::theme_djpr()
}

# This is also good - returns a {patchwork} object containing subplots
viz_fake_function <- function(data = filter_dash_data(c("A84599665J",
                                                        "A84600028X"))) {
  
  plot_1 <- data %>%
    dplyr::filter(.data$series_id == "A84599665J") %>%
    djpr_ts_linechart() +
    labs(subtitle = "Number of unemployed people in Ballarat (000s)")
  
  plot_2 <- data %>%
    dplyr::filter(.data$series_id == "A84600028X") %>%
    djpr_ts_linechart() +
    labs(subtitle = "Number of unemployed people in Bendigo (000s)")
  
  patchwork::wrap_plots(plot_1, plot_2, ncol = 1)
}
```

These are examples of **bad `viz_` functions** that do not return a single `gg` object:
```{r, eval = FALSE}
# THIS IS NOT OK - doesn't return anything
viz_fake_function <- function(data = filter_dash_data("A84600028X")) {
  my_plot <- data %>%
    djpr_ts_linechart()
}

# THIS IS NOT OK - returns something other than a `gg` object
viz_fake_function <- function(data = filter_dash_data("A84600028X")) {
  my_plot <- data %>%
    djpr_ts_linechart()
  
  data
}

# THIS IS NOT OK - the function makes two plots, but only one is returned
viz_fake_function <- function(data = filter_dash_data(c("A84599665J",
                                                        "A84600028X"))) {
  
  plot_1 <- data %>%
    dplyr::filter(.data$series_id == "A84599665J") %>%
    djpr_ts_linechart() +
    labs(subtitle = "Number of unemployed people in Ballarat (000s)")
  
  data %>%
    dplyr::filter(.data$series_id == "A84600028X") %>%
    djpr_ts_linechart() +
    labs(subtitle = "Number of unemployed people in Bendigo (000s)")
}

# THIS IS NOT OK - the function returns a list of `gg` objects
viz_fake_function <- function(data = filter_dash_data(c("A84599665J",
                                                        "A84600028X"))) {
  
  plot_1 <- data %>%
    dplyr::filter(.data$series_id == "A84599665J") %>%
    djpr_ts_linechart() +
    labs(subtitle = "Number of unemployed people in Ballarat (000s)")
  
  plot_2 <- data %>%
    dplyr::filter(.data$series_id == "A84600028X") %>%
    djpr_ts_linechart() +
    labs(subtitle = "Number of unemployed people in Bendigo (000s)")
  
  list(plot_1, plot_2)
}

```


## Shiny conventions 
Each `viz_` function produces a chart. These charts must be used somewhere on the Shiny dashboard. Like in any Shiny app, it is required that each chart has a unique identifier, which is used to connect the UI and server side of the app. 

**We use the name of the relevant function without the `viz_` prefix as the unique identifier for Shiny.** For example, the unique identified for the `viz_ind_emppop_state_slope()` function is `"ind_emppop_state_slope"`. 

Most charts are added to the dashboard using the `djpr_plot_server()` and `djpr_plot_ui()` functions. These live in the `{djprshiny}` package. These are the two components of a Shiny module that creates a chart environment with some standard features, including a download button, and an optional date slider and checkbox. This Shiny module turns a ggplot2 object into a responsive htmlwidget using the `ggiraph::girafe()` function. 

UI code lives in files that start with `page_`. For example, the UI of the Indicators page of the dashboard lives in `page_indicators.R`. Within this file, we add code like this:

```{r, eval = FALSE}
djpr_plot_ui("ind_emppop_state_slope")
```

Server-side code lives in `labour_app.R`. Within this file, we add code like this:

```{r, eval = FALSE}
djpr_plot_server(id = "ind_emppop_state_slope",
                 plot_function = viz_ind_emppop_state_slope,
                 date_slider = FALSE,
# plt_change informs the Shiny module about changes in the browser size, to assist with correct re-sizing of the graph when the window changes size
                 plt_change = plt_change,
                 data = filter_dash_data(c(
                   "A84423272J",
                   "A84423356T",
                   "A84423286W",
                   "A84423370L",
                   "A84423328J",
                   "A84423300F",
                   "A84423314V",
                   "A84423342C"
                   )))
```


