---
title: "DJPR Labour Force Summary"
# author: "DJPR SPP Data + Analytics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  officedown::rdocx_document:
    reference_docx: !expr system.file('djpr_word_template.docx', package = 'djprshiny')
    page_size:
      width: 8.3
      height: 11.7
      orient: "portrait"
    page_margins:
      bottom: 0.3
      top: 0.5
      left: 0.5
      right: 0.5
    tables:
      layout: autofit
      caption:
        style: 'Heading 3'
        pre: 'Table '
        sep: ': '
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(officedown)
library(flextable)
pkgload::load_all()

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  error = FALSE,
  warning = FALSE
  )
```
```{r load-data}

dash_data <- load_dash_data()

Sys.setenv("R_DJPRLABOURDASH_TABLEDEST" = "briefing")
```


```{r}
table_overview() 
```

<br>

```{r}
table_gr_sex()
```

<br>

```{r}
table_ind_unemp_state()
```

\newpage

## Youth
Youth labour market data provides insights into headline figures. Youth labour force data is volatile therefore DJPR smooths the data by using 12-month averages. While this assists in observing underlying trends, it makes large month-to-month changes in underlying conditions 
less apparent. 

```{r}
table_gr_youth_summary()
```

\newpage

```{r}
table_gr_youth_unemp_region()
```

\newpage

## Regional Victoria
Regional labour force data is volatile, therefore DJPR and other VPS agencies smooth the data by using 3-month averages. While this assists in observing underlying trends, it makes large month-to-month changes in underlying conditions less apparent. 
