---
title: "DJPR Jobs Summary"
author: "DJPR SPP Data + Analytics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  officedown::rdocx_document:
    reference_docx: !expr system.file('djpr_word_template.docx', package = 'djprshiny')
    toc: T
    page_size:
      width: 8.3
      height: 11.7
      orient: "portrait"
    page_margins:
      bottom: 0.3
      top: 0.5
      left: 0.5
      right: 0.5
    tables:
      layout: autofit
      caption:
        style: 'Heading 3'
        pre: 'Table '
        sep: ': '
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(officedown)
library(flextable)
library(djprshiny)
pkgload::load_all()

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  error = FALSE,
  warning = FALSE,
  tab.topcaption = TRUE
  )

table_split <- function(tbl){
  title <- tbl$caption$value
  tbl$caption <- NULL
  
  return(list(tbl = tbl,
              title = title))
}

```

```{r load-data}

dash_data <- get_dash_data()
Sys.setenv("R_DJPRLABOURDASH_TABLEDEST" = "briefing")
```

## [Overview]{.ul}

```{r, summary-data}

df <- filter_dash_data(
  c("A84423354L",
    "A84423349V",
    "A84423357V",
    "pt_emp_vic",
    "A84423350C",
    "A84423355R",
    "A84426256L",
    "A85223450L",
    "A85223451R",
    "A84424691V"),
  df = dash_data
)

df <- df %>%
  dplyr::filter(.data$series_id == "A84424691V") %>%
  dplyr::mutate(value = slider::slide_mean(.data$value,
                                           before = 11L,
                                           complete = TRUE),
                series_id = "smoothed_youth_unemp") %>%
  dplyr::filter(!is.na(.data$value)) %>%
  dplyr::bind_rows(df)

summ_data <- ts_summarise(df)

```

```{r, summar-dot-point-fn}
# Function to return dot point text for a given series ID
summ_dot_point <- function(series_id) {
  prev <- get_summ(series_id, prev_value, summ_data) %>% 
    round2(1)
  curr <- get_summ(series_id, latest_value, summ_data) %>%
    round2(1)
  
  
  curr_date <- get_summ(series_id, latest_date, summ_data) %>%
    format("%B %Y")
  unit <- get_summ(series_id, unit, summ_data)
  
  if (unit != "Percent") {
    prev <- pretty_round(prev)
    curr <- pretty_round(curr)
  }
  
  raw_diff <- get_summ(series_id, d_period_abs, summ_data)
  diff_sign <- raw_diff %>%
    round2(1) %>%
    sign()
  
  diff <- dplyr::if_else(unit == "000",
                         pretty_round(abs(raw_diff)),
                         as.character(round2(abs(raw_diff), 1)))
  perc_diff <- get_summ(series_id, d_period_perc, summ_data) %>%
    abs() %>%
    round2(1)
  
  out <- dplyr::case_when(
    diff_sign == 0 ~ paste0(" remained at ", curr),
    diff_sign == -1 ~ paste0(" fell from ", prev, 
                            " to ", curr),
    diff_sign == 1 ~ paste0(" rose from ", prev,
                            " to ", curr)
  )
  
  if (unit == "Percent") {
    out <- paste0(out, " per cent")
  }
  
  out <- dplyr::case_when(
    diff_sign == 0 ~ out,
    diff_sign == -1 ~ paste0(out, ", a fall of ", diff),
    diff_sign == 1 ~ paste0(out, ", a rise of ", diff)
  )
  
    if (unit == "Percent") {
    out <- paste0(out, " percentage points")
    } else {
    out <- paste0(out, " workers")
  }
  
  out
}



dot_points <- c(
  glue::glue("-   Victoria's unemployment rate {summ_dot_point(\"A84423354L\")};"),
  glue::glue("-   The number of people employed in Victoria {summ_dot_point(\"A84423349V\")};")
)



```







```{r ft-emp-dot-points}
ftemp_raw_diff <- get_summ("A84423357V", d_period_abs, summ_data)
ftemp_perc_diff <- get_summ("A84423357V", d_period_perc, summ_data) %>%
  round2(1)
ftemp_sign <- sign(ftemp_raw_diff)
ftemp_pretty_diff <- ftemp_raw_diff %>% abs() %>% pretty_round()
ftemp_text <- dplyr::case_when(
  ftemp_sign == 0 ~ " remained unchanged",
  ftemp_sign == -1 ~ paste0(" fell by ", ftemp_pretty_diff, " workers (",
                            ftemp_perc_diff, "%)"),
  ftemp_sign == 1 ~ paste0(" rose by ", ftemp_pretty_diff, " workers (",
                            ftemp_perc_diff, "%)")
)

ptemp_raw_diff <- get_summ("pt_emp_vic", d_period_abs, summ_data)
ptemp_perc_diff <- get_summ("pt_emp_vic", d_period_perc, summ_data) %>%
  round2(1)
ptemp_sign <- sign(ptemp_raw_diff)
ptemp_pretty_diff <- ptemp_raw_diff %>% abs() %>% pretty_round()
ptemp_text <- dplyr::case_when(
  ptemp_sign == 0 ~ " remained unchanged",
  ptemp_sign == -1 ~ paste0(" fell by ", ptemp_pretty_diff, " workers (",
                            ptemp_perc_diff, "%)"),
  ptemp_sign == 1 ~ paste0(" rose by ", ptemp_pretty_diff, " workers (",
                            ptemp_perc_diff, "%)")
)

dot_points <- c(
  dot_points,
  glue::glue("    -   Full-time employment {ftemp_text};"),
  glue::glue("    -   Part-time employment {ptemp_text};"),
  glue::glue("-   The number of unemployed people in Victoria {summ_dot_point(\"A84423350C\") %>% gsub(\"workers\", \"people\", .)};"),
  glue::glue("-   Victoria's participation rate {summ_dot_point(\"A84423355R\")};")
)



```




```{r hours-worked}
hours_change <- get_summ("A84426256L", d_period_perc, summ_data) %>%
  round2(1)
hours_sign <- sign(hours_change)
hours_text <- dplyr::case_when(
  hours_sign == 0 ~ " didn't change",
  hours_sign == -1 ~ paste0(" fell by ", abs(hours_change), "%"),
  hours_sign == 1 ~ paste0(" rose by ", abs(hours_change), "%")
)


dot_points <- c(
  dot_points,
  glue::glue("-   The total number of hours worked in Victoria {hours_text};"),
  glue::glue("-   Victoria's underemployment rate {summ_dot_point(\"A85223450L\")};"),
  glue::glue("-   The youth unemployment rate in Victoria ",
             summ_dot_point("smoothed_youth_unemp"),
             " (smoothed using a 12-month rolling average);"),
  glue::glue("-   The unsmoothed, original youth unemployment rate is ",
             get_summ("A84424691V", latest_value, summ_data) %>% round2(1),
             " percent, compared to ",
             get_summ("A84424691V", prev_value, summ_data) %>% round2(1),
             " percent a month earlier.")
)



```




```{r dotpoint render, results='asis'}
cat(
  paste(dot_points, collapse = '\n')
)

# save to md for inclusion in email
writeLines(dot_points, 'dotpoints.md')
```

\newpage

```{r, results='asis'}
t1 <- table_overview() |>
  table_split()
```

### Table 1: `r t1$title`

`r t1$tbl`






\newpage

```{r}
t2 <- table_gr_sex() |>
  table_split()

```

### Table 2: `r t2$title`

`r t2$tbl`



```{r}
t3 <- table_ind_unemp_state() |>
  table_split()
```

<br>

### Table 3: `r t3$title`

`r t3$tbl`






\newpage

## [Youth]{.ul}

Youth labour market data provides insights into headline figures. Youth labour force data is volatile therefore DJPR smooths the data by using 12-month averages. While this assists in observing underlying trends, it makes large month-to-month changes in underlying conditions less apparent.

```{r}
t4 <- table_gr_youth_summary() |>
  table_split()
```

### Table 4: `r t4$title`

`r t4$tbl`






\newpage

```{r}
t5 <- table_gr_youth_unemp_region() |>
  table_split()
```

### Table 5: `r t5$title`

`r t5$tbl`






\newpage

## [Metropolitan Melbourne]{.ul}

```{r}
t6 <- table_reg_metro_states_unemprate() |>
  table_split()
```

### Table 6: `r t6$title`

`r t6$tbl`

<br>




```{r}
t7 <- table_reg_metro_emp() |>
  table_split()
```

### Table 7: `r t7$title`

`r t7$tbl`

<br>




```{r}
t8 <- table_reg_metro_unemp() |>
  table_split()
```

### Table 8: `r t8$title`

`r t8$tbl`

<br>




```{r}
t9 <- table_reg_metro_unemprate() |>
  table_split()
```

### Table 9: `r t9$title`

`r t9$tbl`

<br>





```{r}
t10 <- table_reg_metro_partrate() |>
  table_split()
```

### Table 10: `r t10$title`

`r t10$tbl`





\newpage

## [Regional Victoria]{.ul}

```{r}
t11 <- table_reg_nonmetro_states_unemprate() |>
  table_split()
```

### Table 11: `r t11$title`

`r t11$tbl`

<br>




```{r}
t12 <- table_reg_nonmetro_emp() |>
  table_split()
```

### Table 12: `r t12$title`

`r t12$tbl`






\newpage

```{r}
t13 <- table_reg_nonmetro_unemp() |>
  table_split()
```

### Table 13: `r t13$title`

`r t13$tbl`

<br>




```{r}
t14 <- table_reg_nonmetro_unemprate() |>
  table_split()
```

### Table 14: `r t14$title`

`r t14$tbl`




```{r}
t15 <- table_reg_nonmetro_partrate() |>
  table_split()
```

### Table 15: `r t15$title`

`r t15$tbl`






\newpage

## [Industries]{.ul}

```{r}
t16 <- table_industries_summary() |>
  table_split()
```

### Table 16: `r t16$title`

`r t16$tbl`
